Price of Anarchy for Mean Field Games

### 2018-08-03 PoA.tex
E(xi) \neq 0 not \neq 1

\begin{remark}
	Assume (\ref{eq:assumptions}) and $\lambda=1$. Then Theorem \ref{thm:PoA_equivalent_1} tells us that the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$. To see this, assume $PoA=1$. Since $\lambda=1$, we have $c^{MFG}=c^{MKV}$ and thus, condition (\ref{eq:prop_1_2}) holds. If $\mathbb{E}(\xi)=0$, clearly conditions (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) hold, as noted in Corollary \ref{corollary_2}. If $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1=0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ and $C^u=C^w$ which together with $\lambda=1$ imply conditions (\ref{eq:prop_1_1}) and (\ref{eq:prop_1_3}), similarly as Corollary \ref{corollary_1}. Now, if $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1>0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ which implies condition (\ref{eq:prop_1_3}). Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}). In particular, recall from Remark \ref{remark_2} that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
\end{remark}

>>>>

\begin{remark}
	Assume (\ref{eq:assumptions}) and $\lambda=1$. Then Theorem \ref{thm:PoA_equivalent_1} tells us that the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$. To see this, assume $PoA=1$. Since $\lambda=1$, we have $c^{MFG}=c^{MKV}$ and thus, condition (\ref{eq:prop_1_2}) holds. If $\mathbb{E}(\xi)=0$, clearly conditions (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) hold, as noted in Corollary \ref{corollary_2}. If $\mathbb{E}(\xi) \neq 0$ and $\bar{b}_1=0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ and $C^u=C^w$ which together with $\lambda=1$ imply conditions (\ref{eq:prop_1_1}) and (\ref{eq:prop_1_3}), similarly as Corollary \ref{corollary_1}. Now, if $\mathbb{E}(\xi) \neq 0$ and $\bar{b}_1>0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ which implies condition (\ref{eq:prop_1_3}). Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}). In particular, recall from Remark \ref{remark_2} that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
\end{remark}
